
```{r, echo=FALSE,results='hide',message=FALSE}
library(licor, quietly=TRUE, verbose=FALSE)
library(stringr)
if(is.null(data)){
  #fn = "../files/out1.xlsx"
  #wb = loadWorkbook(fn)
  #data = readWorksheet(wb,"Joined Licor data")
  #smry = readWorksheet(wb,"Summary Licor data")
} else {
  fn = basename(data$filename)
  smry = summary.licor(data)
  data = join.markers(data)
}
nal = ncol(data)-1 # Number of alleles
```

Licor marker report for file: `r fn`
========================================================


There were **`r nrow(data)`** samples in the joined marker matrix. The matrix has a total of **`r nal`** alleles across a total of **`r nrow(smry)`** markers.

Summary of the marker data in the original file:

```{r results='asis',echo=FALSE}
library(xtable) 
print(xtable(smry), type='html') 
```

### Duplicated individuals across all alleles

```{r results='hide', echo=FALSE}

mprof = apply(data[,2:ncol(data)],1,paste,collapse="")
ndups = length(which(duplicated(mprof)))
ndpct = round((ndups/nrow(data)*100), 0)
gdups = data$Genotype[duplicated(mprof)]

```
There are **`r ndups` (`r ndpct`)%** duplicated genotypes (having exactly the same molecular profile). They are (omitting the first occurence): 

`r paste(gdups, collapse=', ')`.



```{r run-all,include=FALSE}
out = NULL
fcn = "../reports/child.Rmd"
for(x in 1:nrow(smry)){
  out = c(out,knit_child(fcn))
}
```

`r paste(out, collapse = "\n")`

